Inefficient Concessions and Mediation

### 2016-09-27 draft.tex
format draft to compile independently and revise abstract

%\documentclass[12pt, letterpaper]{article}
%\usepackage{graphicx}
%\usepackage{moreverb}
%\usepackage{mdwlist}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage[hmargin=1in,vmargin=1in]{geometry}
%\usepackage[left=0.9in,top=0.9in,right=0.9in,nohead]{geometry}

%\newcommand{\be}{\begin{equation}}
%\newcommand{\ee}{\end{equation}}
%\newcommand{\bi}{\begin{itemize*}}
%\newcommand{\ei}{\end{itemize*}}
%\newcommand{\bgd}{\begin{gathered}}
%\newcommand{\egd}{\end{gathered}}
%\newcommand{\bgr}{\begin{gather}}
%\newcommand{\edgr}{\end{gather}}
%\newcommand{\mb}{\mathbf}
%\newcommand{\ve}{\varepsilon}
%\newcommand{\real}{\mathbb{R}}
%\newcommand{\de}{\delta}
%  \usepackage{setspace}
%  \doublespacing

%\thispagestyle{empty}

%\begin{document}\title{Inefficient Concessions and Mediation} 
%\author{ Ben Horne}
%To Do : define what is ineffieicncy
%\maketitle

%\section{Abstract}
%We explore a model of bilateral conflict, examining the role of concessions as signals, in addition to being ends in themselves. In doing so, we open up a rationale for mediation: to remove the inefficiencies of signaling in the pre-play round of negotiations. Two parties are engaged in conflict, manifested as the stage game Nash equilibrium of a repeated Prisoner's Dilemma. Each party distrusts the other's willingness to pursue peace, and can indicate its own willingness through costly signaling, i.e. concessions. In resolving this trust issue and attempting to end the conflict, efficient concessions are generally preferred, but optimal signaling can include inefficiency if concessions can later be used against the giving party.  Under such scenarios, a third party mediator can sometimes reduce inefficiency and improve welfare, and we give an explanation for the mechanism that makes mediation effective.
%Two parties are engaged in conflict, and each distrusts the other's willingness to pursue peace. Each can indicate its own interest in peace through costly signaling, or concessions. In certain environments, however, a lack of trust means that optimal concessions are not made, creating inefficiencies in the negotiation that can reduce the possibility of peace. Through a formal model, we explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace. In this process, we open up a rationale for mediation: to remove the inefficiencies of signaling in a preliminary round of negotiations.
 %   Results show that in bilateral negotiation, parties may prefer to give inefficient concessions due to the other party’s potential power to hurt. Additionally, conditions are shown under which a party be willing to, or even prefer to, give the first concession rather than waiting or giving simultaneously.    ...gain insight into the usefulness of concessions in making peace between warring factions. 
%\newpage

\section{Introduction and motivation} %LAKE For instance, the problem you begin with in the cases of Israel/Syria and West Bank are well understood as bargaining over assets that confer future power. But this is not understood as a problem of private information, as you treat it here, but as one of credible commitment. Its not clear how your types map onto the commitment problem. HOW: THAT TYPES COULD CHANGE OVER TIME?

@@

\captionof{table}{Stage Game Payoffs}
\begin{center}
\begin{tabular}{|l|c|c|}
  \hline      & Trust & Fight \\ \hline
	 Trust& T, T& -D, T+W \\ \hline
	Fight & T+W,-D& W-D, W-D \\ \hline
\end{tabular}
\end{center}

@@

In period 0, after receiving his concession, a country makes the decision to allocate it between military and civil society. $\alpha_i$ is the portion of his received concession that country i chooses to dedicate to civil society; $(1- \alpha_i$) is the portion country i dedicates to military buildup. This decision is a simple optimization problem for each country. Parameters are common knowledge so the result of this decision is well known should the country's type be known. Concessions are immediately converted into civil society or military gifts and incorporated into payoff functions. 
 $C_h(\cdot)=C_l(\cdot)=1$ as earlier in the model description. Periods 1 to $\infty$ are as before but with the following stage game payoffs:
\newpage
\captionof{table}{Modified Stage Game Payoffs}
\begin{center}

@@

\newpage
\section{Bibliography} %can add search(kaplan), expoeriments (2) and workplace gift exchange papers (the "gift giving as a medium" explanation
\ssp
\begin{list}{}{\setlength{\leftmargin}{0.0in}\setlength{\rightmargin}{0.0in}\setlength{\itemindent}{0.0in}\setlength{\itemsep}{0.05in}}

@@

%\end{document}

>>>>

\documentclass[12pt, letterpaper]{article}
\usepackage{graphicx}
\usepackage{moreverb}
\usepackage{mdwlist}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{verbatim}
\usepackage[hmargin=1in,vmargin=1in]{geometry}
%\usepackage[left=0.9in,top=0.9in,right=0.9in,nohead]{geometry}

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bi}{\begin{itemize*}}
\newcommand{\ei}{\end{itemize*}}
\newcommand{\bgd}{\begin{gathered}}
\newcommand{\egd}{\end{gathered}}
\newcommand{\bgr}{\begin{gather}}
\newcommand{\edgr}{\end{gather}}
\newcommand{\mb}{\mathbf}
\newcommand{\ve}{\varepsilon}
\newcommand{\real}{\mathbb{R}}
\newcommand{\de}{\delta}
  \usepackage{setspace}
  \doublespacing

\thispagestyle{empty}

\title{Inefficient Concessions and Mediation} 
\author{Kristy Buzard\\
Syracuse University \\
kbuzard@syr.edu\\
Ben Horne\\ 
University of California, San Diego}
%To Do : define what is ineffieicncy

\begin{document}
\maketitle

\begin{abstract}
When two parties are engaged in conflict and each distrusts the other's willingness to pursue peace, concessions can be used to indicate an interest in making peace. We demonstrate that a lack of trust can prevent optimal concessions from being made, creating inefficiencies in negotiation that can reduce the possibility of peace. We use a game-theoretic model to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace. In this process, we open up a rationale for mediation: to remove the inefficiencies of signaling in a preliminary round of negotiations. 
\end{abstract}

\section{Introduction} %LAKE For instance, the problem you begin with in the cases of Israel/Syria and West Bank are well understood as bargaining over assets that confer future power. But this is not understood as a problem of private information, as you treat it here, but as one of credible commitment. Its not clear how your types map onto the commitment problem. HOW: THAT TYPES COULD CHANGE OVER TIME?

@@

%\captionof{table}{Stage Game Payoffs}
\begin{center}
\begin{tabular}{|l|c|c|}
  \hline      & Trust & Fight \\ \hline
	 Trust& T, T& -D, T+W \\ \hline
	Fight & T+W,-D& W-D, W-D \\ \hline
\end{tabular}
\end{center}

@@

In period 0, after receiving his concession, a country makes the decision to allocate it between military and civil society. $\alpha_i$ is the portion of his received concession that country i chooses to dedicate to civil society; $(1- \alpha_i$) is the portion country i dedicates to military buildup. This decision is a simple optimization problem for each country. Parameters are common knowledge so the result of this decision is well known should the country's type be known. Concessions are immediately converted into civil society or military gifts and incorporated into payoff functions. 
 $C_h(\cdot)=C_l(\cdot)=1$ as earlier in the model description. Periods 1 to $\infty$ are as before but with the following stage game payoffs:
\newpage
%\captionof{table}{Modified Stage Game Payoffs}
\begin{center}

@@

\newpage
\section{Bibliography} %can add search(kaplan), expoeriments (2) and workplace gift exchange papers (the "gift giving as a medium" explanation

\begin{list}{}{\setlength{\leftmargin}{0.0in}\setlength{\rightmargin}{0.0in}\setlength{\itemindent}{0.0in}\setlength{\itemsep}{0.05in}}

@@

\end{document}
